The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-08-08 article.tex

  \subsection*{Signatures}

  An implementation has been provided of the Signature structure descriptor for
  molecules~\cite{Faulon2003}. These act as a linear notation - like the SMILES format - 
  for the whole molecule as well as for connected substructures rooted at a single atom. The 
  descriptor can also be canonicalized to provide isomorphism-independent
  representations~\cite{Faulon2004}.

@@

OSGi bundles are available for the CDK too, which are used by Bioclipse and
KNIME.

% ping Arvid

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
The authors acknoledge the great number of people who have contributed smaller
and larger contributions to the CDK library. A full list of contributors is
found in the AUTHORS file~\cite{AUTHORS}.

>>>>

  \subsubsection*{Signatures}

  An implementation has been provided of the Signature structure descriptor for
  molecules~\cite{Faulon2003}. These act as a linear notation - like the SMILES format - 
  for the whole molecule as well as for connected substructures rooted at a single atom. The 
  descriptor can also be canonicalized to provide isomorphism-independent
  representations~\cite{Faulon2004}, and has been successfully used in QSAR modeling~\cite{signaturefingerprints,Spjuth2011DS,Moghadam2015,Alvarsson2014,Spjuth2012OS,Norinder2013}.

@@

OSGi bundles are available for the CDK too, which are used by e.g. Bioclipse~\cite{spjuth2007bioclipse,spjuth2009bioclipse} and KNIME~\cite{Beisken2013}. Due to split packages between CDK modules, CDK is bundled as a single OSGi jar, which is available from \url{http://pele.farmbio.uu.se/bioclipse/cdk/cdk-1.5.13/}. This constitutes an area where improvements can be done on modularization.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
The authors acknowledge the great number of people who have contributed smaller
and larger contributions to the CDK library. A full list of contributors is
found in the AUTHORS file~\cite{AUTHORS}. OS acknowledges support from the Swedish strategic research programs eSSENCE and Swedish e-Science Research Center (SeRC).
